---
title: "607_project1"
author: "Mengqin Cai"
date: "9/22/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project1

In this project, you’re given a text file with chess tournament results where the information has some structure. Your job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) with the following information for all of the players:
Player’s Name, Player’s State, Total Number of Points, Player’s Pre-Rating, and Average Pre Chess Rating of Opponents
For the first player, the information would be:
Gary Hua, ON, 6.0, 1794, 1605
1605 was calculated by using the pre-tournament opponents’ ratings of 1436, 1563, 1600, 1610, 1649, 1663, 1716, and dividing by the total number of games played.

## Import Data

```{r data }

tournament <- readLines("https://raw.githubusercontent.com/DaisyCai2019/Homework/master/tournamentinfo.txt")

head(tournament)

```

## Extraction 
```{r extraction}
require(stringr)


#Player’s Name
name<-unlist(str_extract_all(tournament, "\\w+[^USCF|a-z] ?\\w+ \\w+"))
name

#Player’s State. We only have ON, MI and OH three states
state<-unlist(str_extract_all(tournament, "( MI )|( OH )|( ON )"))
state

#Total Number of Points
point<-unlist(str_extract_all(tournament, "\\d\\.\\d"))
point

#Player’s Pre-Rating 


#extract information and remove "R:"
preRating<-str_replace(unlist(str_extract_all(tournament, "(R:\\s*)(\\d+)")),"R: ","")

#change to number
preRating<-as.numeric(preRating)
preRating


#Average Pre Chess Rating of Opponents
avgRating<-unlist(str_extract_all(tournament,  "\\|[0-9].*"))


#Replace all the blanks without opponents’ information with 00 and extract the number
avgRating <- str_extract_all(str_replace_all(avgRating, "\\s{1,2}\\|","00|"),"\\s\\d{1,2}")


#change it to matrix and number
avgRating <- matrix(unlist(avgRating),byrow=TRUE, nrow=length(avgRating) )
avgRating <- t(apply(avgRating,1,as.numeric)) 

#Loop through the whole avgRating number to replace the opponents’ number with their actual rating. 

for (i in 1:nrow(avgRating)) {
  for (j in 1:ncol(avgRating)){
    if (avgRating[i,j] == 0){
      avgRating[i,j] = NA
    }
  else{avgRating[i,j] <- preRating[avgRating[i,j]]}
  }
}

#Caculate the Rating of Opponents
avgRating <- c(rowMeans(avgRating, na.rm = TRUE))
avgRating<-round(avgRating,0)
avgRating


```

## Finalize and export all the data

```{r export}
final<-data.frame(name,state,point,preRating,avgRating)
final
write.csv(final, "data607_project1.csv", row.names=FALSE)
```



