---
title: "607_Homework2"
author: "Mengqin Cai"
date: "9/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Description

Choose six recent popular movies.  Ask at least five people that you know (friends, family, classmates, imaginary friends) to rate each of these movie that they have seen on a scale of 1 to 5.  Take the results (observations) and store them in a SQL database.  Load the information into an R dataframe.


## Load data into R
```{r load data}
library(RMySQL)

drv <- dbDriver("MySQL")
con <- dbConnect(drv, user="root", password = "password", dbname="movie", host="localhost")

```


## Show two tables of data
```{r show-data}

#All the data
sql<-"select a.id, a.title,a.genre,b.personName,b.score
      from movie a inner join review b
      on a.id=b.movieID
     
      order by title
"
df <- data.frame(dbGetQuery(con, sql))
df


#Table with the average rating 

sql2<-"select a.id, a.title, a.genre,avg(score)
      from movie a inner join review b
      on a.id=b.movieID
      group by title
      order by id
      "
df2 <- data.frame(dbGetQuery(con, sql2))
df2

```

## Analysis of the data

We use the bar to compare the average score of the rating.

```{r analysis}

summary(df)
dim(df)


barplot(df2$avg.score.~df2$id, xlab="Movies",ylab="Score",main="Average score of the Rating",names.arg = c("CrazyRich", "GoodBoys", "SpiderMan", "Scary", "BlinkEye", "Overcomer"))
 

```





