---
title: "607HW1"
author: "Mengqin Cai"
date: "8/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Your task is to study the dataset and the associated description of the data (i.e. “data dictionary”). You may need to look around a bit, but it’s there! You should take the data, and create a data frame with a subset of the columns in the dataset. You should include the column that indicates edible or poisonous and three or four other columns. You should also add meaningful column names and replace the abbreviations used in the data—for example, in the appropriate column, “e” might become “edible.” Your deliverable is the R code to perform these transformation tasks.

```{r }
#Read Mushroom Data

library(RCurl)
x <- getURL("https://raw.githubusercontent.com/DaisyCai2019/Homework/master/agaricus-lepiota.csv")
mushrooms <- read.csv(text = x,header=FALSE)

head(mushrooms)
dim(mushrooms)
summary(mushrooms)

#Add column name to the data
names(mushrooms) <- c("edible_poisonous","shape","surface","color","bruises","odor","gill-attachment","gill-spacing","gill-size","gill-color","stalk-shape","stalk-root","stalk-surface-above-ring","stalk-surface-below-ring","stalk-color-above-ring","stalk-color-below-ring","veil-type","veil-color","ring-number","ring-type","spore-print-color","population","habitat")
head(mushrooms)

#subset the data 
mushrooms<-subset(mushrooms,select=c(edible_poisonous,color,odor,habitat))
head(mushrooms)
tail(mushrooms)

#Replace Abbreviations

mushrooms$edible_poisonous <- as.character(mushrooms$edible_poisonous)
mushrooms$edible_poisonous[mushrooms$edible_poisonous == "e"] <- "edible"
mushrooms$edible_poisonous[mushrooms$edible_poisonous == "p"] <- "poisonous"

mushrooms$color <- as.character(mushrooms$color)
mushrooms$color[mushrooms$color == "n"] <- "brown"
mushrooms$color[mushrooms$color == "b"] <- "buff"
mushrooms$color[mushrooms$color == "c"] <- "cinnamon"
mushrooms$color[mushrooms$color == "g"] <- "gray"
mushrooms$color[mushrooms$color == "r"] <- "green"
mushrooms$color[mushrooms$color == "p"] <- "pink"
mushrooms$color[mushrooms$color == "u"] <- "purple"
mushrooms$color[mushrooms$color == "e"] <- "red"
mushrooms$color[mushrooms$color == "w"] <- "white"
mushrooms$color[mushrooms$color == "y"] <- "yellow"



mushrooms$odor <- as.character(mushrooms$odor)
mushrooms$odor[mushrooms$odor == "a"] <- "almond"
mushrooms$odor[mushrooms$odor == "l"] <- "anise"
mushrooms$odor[mushrooms$odor == "c"] <- "creosote"
mushrooms$odor[mushrooms$odor == "y"] <- "fishy"
mushrooms$odor[mushrooms$odor == "f"] <- "foul"
mushrooms$odor[mushrooms$odor == "m"] <- "musty"
mushrooms$odor[mushrooms$odor == "n"] <- "none"
mushrooms$odor[mushrooms$odor == "p"] <- "pungent"
mushrooms$odor[mushrooms$odor == "s"] <- "spicy"


mushrooms$habitat <- as.character(mushrooms$habitat)
mushrooms$habitat[mushrooms$habitat=="g"]<-"grasses"
mushrooms$habitat[mushrooms$habitat=="l"]<-"leaves"
mushrooms$habitat[mushrooms$habitat=="m"]<-"meadows"
mushrooms$habitat[mushrooms$habitat=="p"]<-"paths"
mushrooms$habitat[mushrooms$habitat=="p"]<-"paths"
mushrooms$habitat[mushrooms$habitat=="u"]<-"urban"
mushrooms$habitat[mushrooms$habitat=="w"]<-"waste"
mushrooms$habitat[mushrooms$habitat=="d"]<-"woods"

head(mushrooms)

#subset the data again with some critera
subset(mushrooms,edible_poisonous=="edible" & color=="white" & odor=="anise" & habitat=="meadows")


```




