---
title: "Data607_Homwork_Week9"
author: "Mengqin Cai"
date: "10/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Web APIs

The New York Times web site provides a rich set of APIs, as described here:
https://developer.nytimes.com/apis
You’ll need to start by signing up for an API key.

Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.


# Library

```{r library }
library(httr)
library(jsonlite)
library(dplyr)

```


# Retrieve book data from book API

Define the search date as 2019-01-01 and use fromJSON to generate call. 

```{r book}

key <- "&api-key=76363c9e70bc401bac1e6ad88b13bd1d"
url <- "http://api.nytimes.com/svc/books/v2/lists/overview.json?published_date=2019-01-01"
req <- fromJSON(paste0(url, key))

```

# Output 

Choose the two list of the bestsellers, combine and show the information of author, title, publisher and weeks_on_list. 

```{r}

bestsellers <- req$results$list
category1 <- bestsellers[[1, "books"]]
category2 <- bestsellers[[2, "books"]]
category<-rbind(category1,category2)

subset(category, select = c("author", "title", "publisher","weeks_on_list"))
```

```



















